---
title: "An Interactive Shiny R Markdown Document"
author: "Yihui Xie"
runtime: shiny
---

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
library(shiny)
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       col = 'gray', border = 'white',
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue", lwd = 3)
})
```

## A Monte-Carlo Simulation

When a face is detected from your web camera (if you have one available), the simulation for the value of `pi` will start, otherwise the simulation will pause. The face detection JS library [pico.js](https://github.com/tehnokv/picojs) is used in the demo below. The plots are generated via the R package **plotly**.

```{r, message=FALSE, echo=FALSE}
set.seed(0728)
library(shiny)
library(plotly)
tags$script(src = "www/camvas.js")
tags$script(src = "www/pico.js")
tags$script(src = "www/init.js")
actionButton("button", "Start")

tags$table(tags$tr(
  tags$td(tags$canvas(width = 480, height = 480)),
  tags$td(plotlyOutput("plot1", width = '480px', height = '480px'))
))

plotlyOutput("plot2", height = '300px')

rand = function() runif(1, -1, 1)
x = rand(); y = rand()
dot_sym = function(x, y) {
  I(if (x^2 + y^2 <= 1) 'circle-dot' else 'x')
}
dot_col = function(x, y) {
  I(if (x^2 + y^2 <= 1) 'lightgray' else 'black')
}

sim_pi = function() 4 * mean(x^2 + y^2 <= 1)
s = sim_pi()

p1 = plot_ly(
  x = x, y = y, type = 'scatter', symbol = dot_sym(x, y), color = dot_col(x, y),
  size = 10, mode = 'markers'
) %>%
  layout(
    xaxis = list(range = c(-1, 1)),
    yaxis = list(range = c(-1, 1))
  )

p2 = plot_ly(
  y = s,
  type = 'scatter',
  mode = 'lines',
  line = list(
    color = '#636EFA',
    width = 3
  )
) %>%
  layout(
    yaxis = list(range = c(2.5, 3.5))
  )

output$plot1 = renderPlotly(p1)
output$plot2 = renderPlotly(p2)
proxy1 = plotlyProxy("plot1")
proxy2 = plotlyProxy("plot2")

observe({
  invalidateLater(200)
  d = isolate(input$detected)
  if (input$button > 0 && is.numeric(d) && d == 1) {
    x2 = rand(); y2 = rand()
    x <<- c(x, x2); y <<- c(y, y2)
    s2 = sim_pi()
    proxy1 %>%
      plotlyProxyInvoke("addTraces", list(x = list(x2), y = list(y2), marker = list(symbol = dot_sym(x2, y2), color = dot_col(x2, y2), size = 10)))
    proxy2 %>%
      plotlyProxyInvoke("extendTraces", list(y = list(list(s2))), list(0))
  }
})
```

The R Markdown source document is available at https://github.com/yihui/shiny-apps/tree/master/face-pi.
